% Commonly used by all languages.
\begin{thebibliography}{10}

\bibitem{Artigue}
Artigue, M.: ?`Qu\'e la educaci\'on matem\'atico basada en la
en la indagaci\'on? La Gaceta de la Real Sociedad Matem\'atica Espa\~nola 20(3). 2017.

\bibitem{AbanadesBotanaKovacsRecioSolyomGecse}
Ab\'anades, M.A., Botana, F., Kov\'acs, Z., Recio, T.~and S\'olyom-Gecse, C.:
Development of automatic reasoning tools in GeoGebra.
ACM Communications in Computer Algebra 50(3), p.~85--88.
2016.

\bibitem{BotanaHohenwarterJanicicKovacsPetrovicRecioWeitzhofer}
Botana, F., Hohenwarter, M., Jani\v{c}i\'c, Kov\'acs, Z., Petrovi\'c, I.,
Recio, T.~and Weitzhofer, S.: Automated Theorem Proving in GeoGebra: Current
Achievements. Journal of Automated Reasoning 55.1, p.~39--59. 2015.

\bibitem{BotanaRecio2016}
Botana, F.~and Recio, T.: On the Unavoidable Uncertainty of Truth in Dynamic Geometry Proving.
Mathematics in Computer Science 10(1), p.~5--25. 2016.

\bibitem{BotanaRecio2017}
Botana, F.~and Recio, T.:
Computing envelopes in dynamic geometry environments.
Annals of Mathematics and Artificial Intelligence 80(1), p.~3--20.
2017.

\bibitem{Chou}
Chou, S.-C.: \textit{Mechanical geometry theorem proving.} Kluwer Academic Publishers,
Norwell, MA, USA. 1987.

\bibitem{CoxLittleOShea}
Cox, D.A., Little, J., O'Shea, D.: \textit{Ideals, varieties, and algorithms.
An introduction computational algebraic geometry and commutative algebra.}
4th revised ed. Undergraduate Texts in Mathematics, Springer, Cham. 2015.

\bibitem{Davis}
Davis, P.: The rise, fall, and possible transfiguration of triangle geometry: a mini-history.
The American Mathematical Monthly 102(3), p.~204--214. 1995.

\bibitem{HowsonWilson}
Howson, G.~and Wilson, B.:
\textit{ICMI Study series: School mathematics in the 1990's.} Kuwait: Cambridge University Press. 1986.

\bibitem{Kovacs2015}
Kov\'acs, Z.: \textit{Computer Based Conjectures and Proofs in Teaching Euclidean Geometry}.
PhD thesis. Johannes Kepler University, Linz. 2015.

\bibitem{Kovacs2017}
Kov\'acs, Z.: Automated reasoning Tools in GeoGebra:
A new approach for experiments in planar geometry.
South Bohemia Mathematical Letters 25(1), p.~48--65.
\url{http://home.pf.jcu.cz/~sbml/wp-content/uploads/Kovacs.pdf}. 2017.

\bibitem{KovacsRecioVelez}
Kov\'acs, Z., Recio, T.~and V\'elez, M.P.:
Detecting truth on components. CoRR abs/XXXX.XXXXX. 2018.

\bibitem{KovacsRecioRichardVelez}
Kov\'acs, Z., Recio, T., Richard, P.R.~and V\'elez, M.P.: GeoGebra Automated
Reasoning Tools: A Tutorial with Examples. In: Aldon, G.~and Trgalova, J. (Eds.):
\textit{Proceedings of the 13th International
Conference on Technology in Mathematics Teaching}.
\url{https://hal.archives-ouvertes.fr/hal-01632970}. 2017.

\bibitem{KovacsRecioSolyomGecse}
Kov\'acs, Z., Recio, T.~and S\'olyom-Gecse, C.:
Automatic Rewrites of Input Expressions in Complex Algebraic Geometry Provers.
In: Narboux, J., Schreck, P.~and Streinu, E. (Eds.): \textit{Proceedings of ADG 2016}, p.~137--143. 2016.

\bibitem{Quaresma}
Quaresma, P.: Towards an Intelligent and Dynamic Geometry Book.
Mathematics in Computer Science 11, p.~427--437. 2017.

\bibitem{RecioVelez}
Recio, T.~and V\'elez, M.P.:
Automatic discovery of theorems in elementary geometry.
Journal of Automated Reasoning, 23, p.~63--82.
1999.

\bibitem{RichardOllerMeavilla}
Richard, P.R., Oller, A.M.~and Meavilla, V.:
The Concept of Proof in the Light of Mathematical Work.
ZDM -- The International Journal on Mathematics Education, 48(6), p.~843--859. 2016.

\bibitem{SinclairBartoliniBussiDeVilliersOwens}
Sinclair, N., Bartolini Bussi, M.G., de Villiers, M.~and Owens, K.:
Recent research on geometry education: an ICME-13 survey team report.
ZDM Mathematics Education, 48(5), p.~691--719. 2016.

%\bibitem{ZhouWangSun}
%Zhou, J., Wang, D.~and Sun, Y.: Automated Reducible Geometric Theorem Proving and Discovery by Gr{\"o}bner Basis Method,
%\textit{Journal of Automated Reasoning}, 22 November 2016, ISSN 1573-0670, DOI 10.1007/s10817-016-9395-z. 2016.

\end{thebibliography}
